The Deviation of China Map as a Regression Problem

### 2012-12-05 paper.tex
minor

We first solve the functions in one dimension by setting one parameter to be
constant.
I.e. instead of solving $f_x(x,y)$ directly, we first solve $f_x(x,c)$
and $f_x(c,y)$, where $c$ is a constant.
For example, we will look at $f_x(x,39.36)$ and $f_x(110.16,y)$.
Similarly, we will solve $f_y(x,c)$ and $f_y(c,y)$ before $f_y(x,y)$.

In the following analysis, we will use octave.
All the data used in the analysis has already been posted in my previous
article\footnote{url}.

\section{The four 1D cases}
\subsection{$f_x(const,y)$}
$f_x(const,y)$ looks like to be the simplest, so we solve it first.

@@

\section{The final 2D case: $f_x(x,y)$ and $f_y(x,y)$}
With out too much effort, we have found out the two functions:

@@

To verify the correctness, we can

>>>>

In the following analysis, we will use octave.
All the data used in the analysis has already been posted in my previous
article\footnote{\url{http://wuyongzheng.wordpress.com/2010/01/22/china-map-deviation-as-a-regression-problem/}}.

\section{The four 1D cases}

We first solve the functions in one dimension by setting one parameter to be
constant.
I.e. instead of solving $f_x(x,y)$ directly, we first solve $f_x(x,c)$
and $f_x(c,y)$, where $c$ is a constant.
For example, we will look at $f_x(x,39.36)$ and $f_x(110.16,y)$.
Similarly, we will solve $f_y(x,c)$ and $f_y(c,y)$ before $f_y(x,y)$.
In total, there are four 1D cases.

\subsection{$f_x(const,y)$}
$f_x(const,y)$ looks like to be the simplest, so we solve it first.

@@

\section{The final 2D case: $f_x(x,y)$ and $f_y(x,y)$}
With out too much effort, we can find out the two functions:

@@

To verify the correctness, we can compute the deviated coordinates of Monument
to the People's Heroes given its true coordinates.
